\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{biblatex}
\usepackage{amssymb}
\usepackage{amsmath}
%\addbibresource{bib.bib}
\setlength{\parindent}{0em}
\bibliography{bib}


\title{Recap of general math}
\author{warm up!}
\date{\today}
\linespread{1.5}


%% remove numbering
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother


\begin{document}
	
\maketitle
% https://www.hitbullseye.com/Probability-Examples.php	
\subsection{Example 1}
A coin is thrown 3 times .what is the probability that atleast one head is obtained?
	
\subsection{Example 2}

Find the probability of getting a numbered card when a card is drawn from the pack of 52 cards.	
	
\subsection{Example 3}
What is the probability of getting a sum of 7 when two dice are thrown?
	

\subsection{Example 4}
A box contains three coins: two regular coins and one fake two-headed coin $(P(H)=1)$,

1) You pick a coin at random and toss it. What is the probability that it lands heads up?

2) You pick a coin at random and toss it, and get heads. What is the probability that it is the two-headed coin?
\subsection{Example 5}
% https://sphweb.bumc.bu.edu/otlt/MPH-Modules/BS/BS704_Probability/BS704_Probability6.html
A patient goes to see a doctor. The doctor performs a test with 99 percent reliability -- that is, 99 \% of people who are sick test positive and 99 \% of the healthy people test negative. The doctor knows that only 1 percent of the people in the country are sick. Now the question is: if the patient tests positive, what are the chances the patient is sick?

\subsection{Example 6}
%ttps://www.hackmath.net/en/math-problem/18143?tag_id=151
Using vector dot product calculate the angle of the body diagonals of the cube. (Radinas, angle or cos)

\subsection{Example 7}
Multiply matrices:
\begin{equation}
	\left[
	\begin{array}{cc}
		5 & 1 \\
		4 & 2 \\
		4 & 3 \\
		2 & 4 \\  
	\end{array}
	\right]
	\left[
	\begin{array}{cccc}
		 
		5 & 1 & 99 & -1\\
		8 & 0 & 87 & 0\\
		
	\end{array}
\right]
\end{equation}

\begin{equation}
	\left[
	\begin{array}{cccc}
	
	5 & 1 & 99 & -1\\
	8 & 0 & 87 & 0\\
	
\end{array}
	\right]
	\left[
	\begin{array}{cc}
	5 & 1 \\
	4 & 2 \\
	4 & 3 \\
	2 & 4 \\  
\end{array}
	\right]
\end{equation}

\end{document}