---
title: "R language"
author: Sergey Chuvakin
date: "`r Sys.Date()`"
output: ioslides_presentation
---


# R advanced structures

## Vectors aka arrays

```{r}
v <- c(1,2,3,4) ## basically it's a sequence 
```

```{r}
class(v)
```

```{r}
1:4
```
```{r}
class(1:4) ## dynamic typing
```

## Vector operations

```{r}
v + 1
```

```{r}
v * 2
```

```{r}
a <- c(5,6,7,8)
a + v
```

```{r}
a <- c(5,6,7,8,6)
a + v
```

## Vector operations and slices

```{r}
sum(a) + sum(v)
```

```{r}
a[1]
```

```{r}
a[3:4]
```

```{r}
length(v)
```

## Vector operations and slices 2

```{r}
a[length(a)]
```
```{r}
v[c(TRUE,FALSE,TRUE,FALSE)]
```
```{r}
v %% 2
```
```{r}
v[v %% 2 == TRUE]
```
## Usefull functions

```{r}
rep(1, 5)
```

```{r}
seq(1, 5)
```

```{r}
seq(1, 5, 2)
```

## Matrices

```{r}
matrix(1:9, nrow = 3, ncol = 3)
```

```{r}
matrix(1:9, nrow = 3, ncol = 3, byrow = TRUE)
```

## Matrix operations

```{r}
m <- matrix(1:9, nrow = 3, ncol = 3, byrow = TRUE)
dim(m)
```

```{r}
nrow(m)
```

```{r}
ncol(m)
```

## Matrix names 

```{r}
rownames(m)
```
```{r}
rownames(m) <- c('A', 'B', 'C')
colnames(m) <- c('D', 'E', 'F')
```

```{r}
rownames(m)
```

```{r}
colnames(m)
```
## Matrix names 2

```{r}
m
```

```{r}
dimnames(m)
```

```{r}
dimnames(m) <- NULL
m
```
## Matrix sclices

```{r}
m[2, 3]
```

```{r}
m[2, 3] ## roman catholics
```

```{r}
m[1:2, 3]
```

## Why we need names

```{r}
rownames(m) <- c('A', 'B', 'C')
colnames(m) <- c('D', 'E', 'F')
names(v) <- c('a', 'b', 'c', 'd')
```

```{r}
v['a']
```
```{r}
v[c('a', 'b')]
```
```{r}
m['A', c('D', 'E')]
```

## Data Frames - the most important structure for us!

```{r}
m <- matrix(1:9, nrow = 3, ncol = 3, byrow = TRUE)
data.frame(m)
```
```{r}
rownames(m) <- c('A', 'B', 'C')
colnames(m) <- c('D', 'E', 'F')
data.frame(m)
```

## Data Frames another syntax

```{r}
data.frame(a = c(1,2,3), c = c(4,5,6))
```
```{r}
df <- data.frame(sex = c('Male','Female','Male'), age = c(34,45,16)) ## Example
df
```
## Data Frames operations

```{r}
df['sex'] ## data frame
```
```{r}
df[['sex']]
```

## Data Frames slices

```{r}
df[1,2]
```
```{r}
df[1, 'sex']
```
```{r}
rownames(df) <- c('A', 'B', 'C')
df['B', 'sex']
```

## Common data frame operations

```{r}
dim(df)
```

```{r}
nrow(df)
```

```{r}
ncol(df)
```

```{r}
names(df)
```

## Common data frame operations

```{r}
df$age ## vector
```
```{r}
head(df)
```

```{r}
tail(df)
```
## list

```{r}
list(string = 'A', int = 1, vector = 1:10, dataFrame = df)
```

```{r}
l <- list(string = 'A', int = 1, vector = 1:10, dataFrame = df)
l[1] ## type list
```

```{r}
l <- list(string = 'A', int = 1, vector = 1:10, dataFrame = df)
l[[1]] ## type string
```

```{r}
l <- list(string = 'A', int = 1, vector = 1:10, dataFrame = df)
l$string ## call by name, type string
```

## factors

```{r}
vec <- rep(c('Male', 'Female'), 100)
fac_vec <- as.factor(vec)
```

```{r}
levels(fac_vec)
```



## "Handmade" functions

```{r}
my_foo <- function() {
  print('Hello SAS')
}
```

```{r}
my_foo()
```

```{r}
doubled_sum <- function(x, y) {
  return((x + y) * 2) 
}
```

```{r}
doubled_sum(5,7)
```

##  Loops

```{r}
for (i in 10:20) {
  print(i)
}
```

## Conditions

```{r}
if (1 == 2) {
  print('Mad world')
} else {
  print('Hello world')
}
```

## Conditions and loops

```{r}
for (i in 1:10) {
  if (i %% 2 == 0) {
    print(i)
  }
}
```

# What else??

## Google it!

- strings in R
- apply, sapply, lapply
- Name spaces in R

