---
title: "Practice R language"
author: "Sergey Chuvakin"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

0) Let’s create the following vectors:

u <- 4

v <- 8

Use the elementary arithmetic operators +, -, *, /, and ^ to:

- add u and v
- subtract v from u
- multiply u by v
- divide u by v
- raise u to the power of v

```{r}
### Your code here
```


1) Write a R program to get the first 10 Fibonacci numbers.

```{r}
### Your code here
```

2) Write a R program to print the numbers from 1 to 100 and print "Fizz" for multiples of 3, print "Buzz" for multiples of 5, and print "FizzBuzz" for multiples of both

```{r}
### Your code here
```

3) Write a R program to create three vectors a,b,c with 3 integers. Combine the three vectors to become a 3×3 matrix where each column represents a vector. Print the content of the matrix
(HINT: use function cbind, just type ?cbind)

```{r}
### Your code here
```

4) Write a function that produce a dot product of two vectors

```{r}
### Your code here
```

5) Write a R program to create an empty data frame.

```{r}
### Your code here
```

6) Write a function to calculate this equation
$$n = \frac{ln(\frac{i}{\frac{M}{P} -i} + 1)}{ln(1 + i)}$$
```{r}
mortgage_rate <- function(M, P, i) {
  ### Your code here
}
```

7) Distance between cities!

Suppose you have geographical data and want to calculate the distance between two places on earth, given by their latitude and longitude coordinates. Consider the coordinates for:

    Paris: 48.8566° N (latitude), 2.3522° E (longitude), and
    New York 40.7128° N (latitude), 74.0060° W (longitude)

If you’re up for a real challenge, lookup “Great-circle distance” on Wikipedia, and use the spherical law of cosines to find the distance (and stop reading right now!).

If this sounds like a pretty daunting task, don’t worry! I will walk you through this step-by-step in the remainder of this exercise.

Ok, here we go. We will use the following common abbreviations:

- latitude  $\phi$ (phi)
- longitude $\lambda$ (lambda)

Create 4 scalars phi.paris, phi.ny, lambda.paris, lambda.ny, representing these coordinates. Because New York is located in the West, you have to enter this as a negative value (-74.0060).

a) Convert the 4 coordinates from degrees to radians, using the formula:
$$radians = degrees \times \frac{\pi}{180}$$
b) Calculate the central angle between both cities, using the spherical law of cosines:
$$\Delta\sigma = arccos(sin\phi_1\times\sin\phi_2 + cos\phi_1\times\cos\phi_2cos(\Delta\lambda))$$
where: $\Delta\sigma$  is just a scalar (name it anything you want in R),
$\phi_1$ is the latitude of Paris,
$\phi_2$ the latitude of New York, and $\Delta\lambda$
the absolute difference between both longitudes.Hint: For this calculation you need the following mathematical functions in R: sin, cos, acos, and abs.
c) Finally, to find the distance, multiply $\Delta\sigma$ 
(i.e., the outcome you just calculated) by the radius of the earth (6371 km.)

```{r}
### Your code here
```
8) Write a function that reverse any words, i.g. 
 - input: cat
 - output: tac
 
 HINT: use functions - rev, strsplit <br>
 HINT2: use '' as separator in strsplit
 
```{r}
### Your code here
```
