---
title: "PRACTICE!!"
author: "Sergey Chuvakin"
date: "11/4/2020"
output: html_document
---

## Dplyr

Read tha data IQ_brain.csv. 

It's real research was taken here: “The Data and Story Library” http://lib.stat.cmu.edu/DASL/

Description:

20 men and 20 women were studied. Data contains some phisical data, three types of IQ tests and size of brain (MRINACount). 

Answer the following questions. 
1) How many rows and columns here?
2) What the columns here? 
3) How many missings here. (HINT: is.na gives TRUE)
4) Show the 5 smartest people according one the test (pick random one)
5) Create one more dataset, where will be gender of person, one IQ test and size of the brain
6) Whose brain larger in average? Man or Woman?
7) Whose IQ is higher above men and women?
8) Do you think it's dependent variables?
9) Show the woman with largest brain
10) Show the man with the highest IQ

```{r}
#### YOUR CODE HERE
```


## GGPLOT

Use the same data and make following plots 

1) Histogram of all IQ test faceted by gender.
2) scatter plot of some IQ test versus MRINACount. colored and faceted by gender
3) Line plot Height vs Brain size faceted and colored by gender

```{r}
#### YOUR CODE HERE

library(ggplot2)
library(dplyr)

read.csv('IQ_brain.csv')
```
