---
title: "FlexDashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---

# Page 1

## Column 1 {.tabset}

### Outline

```{r include=FALSE}
library(ggplot2)
library(dplyr)
library(plotly)

df <- titanic::titanic_train
```

- historgram
- line plot
- scatterplot
- 3D plot
- boxplot 
- map
- flexdashboard

### Glimpse on data

```{r}
glimpse(df)
```

### Basic Hist

```{r}
plotly::plot_ly(x = df$Pclass, 
                type = 'histogram', 
                histnorm = "probability")
```

### Horizontal Hist

```{r}
plotly::plot_ly(y = df$Pclass, 
                type = 'histogram', 
                histnorm = "probability")
```

### Double Hist


```{r}
plotly::plot_ly(y = df$Pclass, 
                type = 'histogram', 
                histnorm = "probability",
                name = 'my_name_0') %>% 
  add_trace(type = 'histogram',
            y = df$Survived,
            bingroup = 1, 
            name = 'my_name_1', 
            opacity = 0.5)
```
See for more information: https://plotly.com/r/histograms/

### Bokeh Hist

```{r}
library(rbokeh)
rbokeh::renderRbokeh({
  df <- titanic::titanic_train
  figure(width = 500, height = 300) %>% 
    ly_hist(Pclass, data = df, breaks = 40, freq = FALSE)
  })
```

### Basic Line Plot
```{r include=F}
setwd('/Users/serge/Desktop/SAS_QM/SAS_Quantitative_Methods/week8/')

climate <- read.csv('DailyDelhiClimateTrain.csv')
```

```{r include=F}
glimpse(climate)
```

```{r}
plotly::plot_ly(climate, x = ~date, y = ~meantemp, type = 'scatter', mode = 'lines')
```

### Double Line

```{r}
plotly::plot_ly(climate, x = ~date, y = ~meantemp, type = 'scatter', mode = 'lines') %>% 
  add_trace(y = ~humidity, name = 'humidity', mode = 'markers') %>% 
  add_trace(y = ~wind_speed, name = 'wind_speed', mode = 'lines')
```

### Bokeh Line Plot

```{r}
library(rbokeh)
rbokeh::renderRbokeh({
  figure(width = 500, height = 300) %>%
    ly_lines(data = climate, x = date, y = meantemp, color = 'blue') %>% 
    ly_lines(data = climate, x = date, y = humidity, color = 'red')
  })
```

### Basic Scatter Plot

```{r}
plot_ly(data = climate, 
        x = ~humidity, 
        y = ~meantemp)
        # marker = list(size = 10,
        #               color = 'rgba(255, 182, 193, .9)',
        #               line = list(color = 'rgba(152, 0, 0, .8)',
        #                           width = 2)))
```

### Bokeh Scatter

```{r}
library(rbokeh)
rbokeh::renderRbokeh({
  figure(width = 500, height = 300) %>%
    ly_points(data = climate, 
              x = humidity, 
              y = meantemp, 
              color = 'blue', 
              hover = humidity)
})
```

### 3D Plot

```{r}
plot_ly(climate, 
        x = ~humidity, 
        y = ~meantemp, 
        z = ~wind_speed)
```

### Basic BoxPlots

```{r}
plot_ly(y = ~df$Fare, type = "box")
```

### Double BoxPlots

```{r}
plot_ly(y = ~df$Fare, type = "box") %>% 
  add_trace(y = ~df$Age, type = "box")
```

### Advanced BoxPlot

```{r}
plot_ly(y = ~df$Fare, 
        type = "box",
        boxpoints = "all",
        jitter = 0.3, 
        pointpos = -1.8) 
```
See more here https://plotly.com/r/box-plots/

### Bokeh BoxPlot
```{r}
library(rbokeh)
rbokeh::renderRbokeh({
  figure(ylab = "Height (inches)", 
         width = 500, 
         height = 300) %>%
    ly_boxplot(humidity, data = climate) # second argument specifies facet
})
```

See more here https://rdrr.io/cran/rbokeh/man/ly_boxplot.html

### Maps

```{r include=F}
df <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/2014_world_gdp_with_codes.csv")
head(df)
```

```{r}
plotly::renderPlotly(
plot_ly(df,
        type='choropleth', 
        locations=df$CODE, 
        z=df$GDP..BILLIONS., 
        text=df$COUNTRY, 
        colorscale="Reds")
)
```
For more info see here: https://plotly.com/r/maps/

